State and Parameter Estimation for Spatio-Temporal Neural Fields

### 2010-04-16 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
paper updates

\begin{itemize}
	\item alternatives to frequency analysis are model selection.
	\item the width of the connectivity basis functions here is known exactly. In practice we don't 
	\item the number of basis functions could be set higher to get a better representation of the field, however this is limited by computation complexity.
	\item Discuss the novelty of using the reduced model (BrainIDE) for creating patient specific models. 
	\item The size of the dentritic arbour is consistent in the cortex.
	\item Spatial frequency of field and the relationship to the required density of electrodes/sensors required for estimation or to capture the required information without aliasing.
	\item The flexibility of the approach
	\item Combining this method with other to incorporate longer range hetrogeneous connectivity.	
	\item The need for activity to perform estimation.
\end{itemize}

>>>>

\begin{itemize}
	\item if we don't know the frequency analysis or the system is marginally sampled or under-sampled, the best we can do is have the basis functions the same as the sensor kernel.
	\item alternatives to frequency analysis are model selection...
	\item the width of the connectivity basis functions here is known exactly. In practice we don't 
	\item the number of basis functions could be set higher to get a better representation of the field, however this is limited by computation complexity.
	\item Discuss the novelty of using the reduced model (BrainIDE) for creating patient specific models. 
	\item The size of the dentritic arbour is consistent in the cortex.
	\item Spatial frequency of field and the relationship to the required density of electrodes/sensors required for estimation or to capture the required information without aliasing.
	\item The flexibility of the approach
	\item Combining this method with other to incorporate longer range hetrogeneous connectivity.	
	\item The need for activity to perform estimation.
\end{itemize}
